% allfont.tex    Test Rotunda fonts
\documentclass{article}
%\documentclass[12pt]{article}
\usepackage{allrtnd}

\newcommand{\romannum}[1]{\romannumeral #1}
\newcommand{\Romannum}[1]{\uppercase\expandafter{\romannumeral #1}}
\newcommand{\ABC}{ABCDEFGHIJKL MNOPQRSTUVWXYZ}
\newcommand{\abc}{abcdefghijkl mnopqrstuvwxyz}
\newcommand{\punct}{.,;:!?`' \&{} () []}
\newcommand{\dashes}{- -- ---}
\newcommand{\figs}{0123456789}
\newcommand{\sentence}{%
this is an example of the rotunda font. now is the time for all good
men, and women, to come to the aid of the party while the quick brown fox
jumps over the lazy dog.}

\newcommand{\Sentence}{%
This is an example of the Rotunda font. Now is the time for all good
men, and women, to come to the aid of the party while the quick brown fox
jumps over the lazy dog.}

\newcommand{\latin}{Te canit adcelebratque polus rex gazifer hymnis.
  Trans zephyrique globum scandunt tua facta per axem.
  Explicit secunda pars summe fratris thome de aquino ordinis fratrum 
  predicatorium, longissima, prolixissima, \& tediosissima scribent;
  Deo gratias, Deo gratias, et iterumm Deo gratias. }

\title{Try Rotunda Fonts}
\author{}
\date{}
%%\pagenumbering{roman}
\begin{document}
\maketitle

\tableofcontents

\section{The character set}

    This provides a short test of the characters in the Rotunda fonts
--- the \verb|rtnd| font family.



\begin{center}
The Rotunda Huge normal font. \\ \par
{\Huge \ABC\\ \abc\\ \punct{}\dashes\\ \figs\\ \par }
\end{center}


\begin{center}
The Rotunda font in its normal size \\
{\ABC{} \abc{} \figs} \\
\end{center}

\begin{center}
The bold normal font, the normal font, and the bold Computer Modern
Roman, all in the normal size \\
{\textbf{\abc{} \figs}} \\
{\abc{} \figs} \\
\textcmr{\textbf{\abc{} \figs}} \\
\end{center}

\begin{center}
The bold versions, in Huge and tiny sizes. \par
\bfseries
\Huge \abc{} \figs \par
\tiny \abc{} \figs \par
\end{center}

\begin{center}
The font in the tiny size \\ \par
{\tiny \ABC{} \\ \abc\\ \figs\\ \par } 
\end{center}

\begin{center}
    Some ligatures in the normal font \\
{``the lazy dog --- but quick fox?''}
\end{center}

\section{Example texts}

    First some well known English phrases in an abcedarian sentence.

\Sentence{}

    After this there are two Latin abecedarian sentences dating from about 
\Romannum{790}, and another sentence from roughly the same period.

\latin{}

    
\textcmss{This is the end of the test file, with this sentence being typeset
using the Computer Modern Sans font in the point size as specified for this
document.}

\end{document}